### 2022-08-11 README.Rmd
DOI
readme update

  - [ICBe_V1_long.Rds](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_data/out/ICBe_V1_long_agreed.Rds)
  - [ICBe_V1.1_long_agreement.Rds](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_data/out/ICBe_V1_wide_agreed.Rds)
      + All coded values individually along with information about how often they were selected by coders.  
      + `ICBe_V1_long.Rds` filtered down only to those codings that were agreed upon (see Algorithm 1 in paper).
  - [ICBe_V1.1_events_agreed_long.Rds](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_data/out/ICBe_V1_wide_agreed.Rds)
    - [ICBe_V1.1_events_agreed.Rds](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_data/out/ICBe_V1_wide_agreed_long.Rds)

      + `ICBe_V1.1_events_agreed.Rds` in wide form where each row is an event.

@@

### License

@@

>>>>

  - [ICBe_V1.1_long.Rds](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_data/out/ICBe_V1.1_long.Rds)
  - [ICBe_V1.1_long_agreement.Rds](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_data/out/ICBe_V1.1_long_agreement.Rds)
      + All coded values individually along with information about how often they were selected by coders.  
      + `ICBe_V1.1_long.Rds` filtered down only to those codings that were agreed upon (see Algorithm 1 in paper).
  - [ICBe_V1.1_events_agreed_long.Rds](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_data/out/ICBe_V1.1_events_agreed_long.Rds)
  - [ICBe_V1.1_events_agreed.Rds](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_data/out/ICBe_V1.1_events_agreed.Rds)

@@

### License and DOI

@@

[![DOI](https://zenodo.org/badge/450249483.svg)](https://zenodo.org/badge/latestdoi/450249483)
